Deciding to Disclose

### 2015-11-10 Results.tex
Figures path

\begin{figure}[H]
\includegraphics[width=100mm]{figures/honesty_plot}
\caption{Average fraction of population ever signalled honestly by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs. Note that the large number of runs leads to very tight confidence intervals.\label{fig:honest_signals}}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=100mm]{figures/honesty_sharing}
\caption{Impact of social learning on trends in the average fraction of population ever signalled honestly by their final appointment, after 1000 rounds, mean with 95\% confidence interval over 100 runs}
\label{fig:honest_sharing}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=90mm]{figures/sharing_emulated_simulated}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
\label{fig:outcome_plots}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=100mm]{figures/unfixed_emu_sig_iqr}
\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
\label{fig:emulated_sharing_iqr}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=100mm]{figures/unfixed_emu_payoff_honesty_group_iqr}
\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}
\label{fig:emulated_payoff_group_iqr}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[width=100mm]{honesty_plot}
\caption{Average fraction of population ever signalled honestly by each appointment, after 1000 rounds, mean with 95\% confidence limit over 1000 runs. Note that the large number of runs leads to very tight confidence intervals.\label{fig:honest_signals}}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=100mm]{honesty_sharing}
\caption{Impact of social learning on trends in the average fraction of population ever signalled honestly by their final appointment, after 1000 rounds, mean with 95\% confidence interval over 100 runs}
\label{fig:honest_sharing}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=90mm]{sharing_emulated_simulated}
\caption{Median moderate drinker signal vs median between drinking type IQR for all decision rules, with signals coded as 0 = light, 1 = moderate, and 2 = heavy.}
\label{fig:outcome_plots}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=100mm]{unfixed_emu_sig_iqr}
\caption{Emulated moderate drinker signal IQR in response to varying \(q_{w}\), and \(w_{w}\)}
\label{fig:emulated_sharing_iqr}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=100mm]{unfixed_emu_payoff_honesty_group_iqr}
\caption{Emulated between groups IQR in response to varying \(s_{i}[a_{i}]:s_{i}[a_{\neg i}]\), and \(x_{h}\)}
\label{fig:emulated_payoff_group_iqr}
\end{figure}
